---
title: "SAT Formulas"
author: "Daniel Olds"
---
# untar sat files: 
```{r}
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
untar("uf50-218.tar.gz")
```

# untar unsat files: 
```{r}
setwd("C:/Users/Daniel Olds/Documents/dimacs/unsat")
untar("uuf50-218.tar.gz")
```

# 80 Formulas: 40 Satisfiable, 40 Unsatisfiable

# Satisfiable Formulas
# 50 Variables, 218 Clauses 

# Formula 1
```{r}
# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-01.cnf') 
open(con);
sat_1 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_1[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_1 <- sat_1[9:226]
sat_1 <- lapply(sat_1, function(x) x[x != "0"])
sat_1 <- lapply(sat_1, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_1 = transform(sat_1)

# Check Literal Count
count(sat_1)

close(con)
```

# Formula 2
```{r}
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")

con <- file('uf50-010.cnf') 
open(con);
sat_2 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_2[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

sat_2 <- sat_2[9:226]
sat_2 <- lapply(sat_2, function(x) x[x != "0"])
sat_2 <- lapply(sat_2, function(x) x[!is.na(x)])

sat_2 = transform(sat_2)
count(sat_2)

close(con)

```

# Formula 3
```{r}
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0100.cnf') 
open(con);
sat_3 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_3[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

sat_3 <- sat_3[9:226]
sat_3 <- lapply(sat_3, function(x) x[x != "0"])
sat_3 <- lapply(sat_3, function(x) x[!is.na(x)])

sat_3 = transform(sat_3)
count(sat_3)

close(con)
```

# Formula 4
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0263.cnf') 
open(con);
sat_4 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_4[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_4 <- sat_4[9:226]
sat_4 <- lapply(sat_4, function(x) x[x != "0"])
sat_4 <- lapply(sat_4, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_4 = transform(sat_4)

# Check Literal Count 
count(sat_4)

close(con)

```

# Formula 5 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0101.cnf') 
open(con);
sat_5 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_5[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_5 <- sat_5[9:226]
sat_5 <- lapply(sat_5, function(x) x[x != "0"])
sat_5 <- lapply(sat_5, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_5 = transform(sat_5)

#Check Literal Count 
count(sat_5)

close(con)

```

# Formula 6 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0102.cnf') 
open(con);
sat_6 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_6[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_6 <- sat_6[9:226]
sat_6 <- lapply(sat_6, function(x) x[x != "0"])
sat_6 <- lapply(sat_6, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_6 = transform(sat_6)

#Check Literal Count 
count(sat_6)

close(con)

```

# Formula 7
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0103.cnf') 
open(con);
sat_7 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_7[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_7 <- sat_7[9:226]
sat_7 <- lapply(sat_7, function(x) x[x != "0"])
sat_7 <- lapply(sat_7, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_7 = transform(sat_7)

#Check Literal Count 
count(sat_7)

close(con)

```

# Formula 8 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0104.cnf') 
open(con);
sat_8 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_8[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_8 <- sat_8[9:226]
sat_8 <- lapply(sat_8, function(x) x[x != "0"])
sat_8 <- lapply(sat_8, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_8 = transform(sat_8)

#Check Literal Count 
count(sat_8)

close(con)

```

# Formula 9
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0105.cnf') 
open(con);
sat_9 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_9[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_9 <- sat_9[9:226]
sat_9 <- lapply(sat_9, function(x) x[x != "0"])
sat_9 <- lapply(sat_9, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_9 = transform(sat_9)

#Check Literal Count 
count(sat_9)

close(con)

```

# Formula 10 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0106.cnf') 
open(con);
sat_10 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_10[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_10 <- sat_10[9:226]
sat_10 <- lapply(sat_10, function(x) x[x != "0"])
sat_10 <- lapply(sat_10, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_10 = transform(sat_10)

# Check Literal Count 
count(sat_10)

close(con)

```

# Formula 11
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0107.cnf') 
open(con);
sat_11 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_11[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_11 <- sat_11[9:226]
sat_11 <- lapply(sat_11, function(x) x[x != "0"])
sat_11 <- lapply(sat_11, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_11 = transform(sat_11)

#Check Literal Count 
count(sat_11)

close(con)

```

# Formula 12
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0108.cnf') 
open(con);
sat_12 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_12[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_12 <- sat_12[9:226]
sat_12 <- lapply(sat_12, function(x) x[x != "0"])
sat_12 <- lapply(sat_12, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_12 = transform(sat_12)

#Check Literal Count 
count(sat_12)

close(con)

```

# Formula 13 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0273.cnf') 
open(con);
sat_13 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_13[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_13 <- sat_13[9:226]
sat_13 <- lapply(sat_13, function(x) x[x != "0"])
sat_13 <- lapply(sat_13, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_13 = transform(sat_13)

#Check Literal Count 
count(sat_13)

close(con)

```

# Formula 14
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0110.cnf') 
open(con);
sat_14 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_14[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_14 <- sat_14[9:226]
sat_14 <- lapply(sat_14, function(x) x[x != "0"])
sat_14 <- lapply(sat_14, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_14 = transform(sat_14)

#Check Literal Count 
count(sat_14)

close(con)

```

# Formula 15
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0111.cnf') 
open(con);
sat_15 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_15[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_15 <- sat_15[9:226]
sat_15 <- lapply(sat_15, function(x) x[x != "0"])
sat_15 <- lapply(sat_15, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_15 = transform(sat_15)

#Check Literal Count 
count(sat_15)

close(con)

```

# Formula 16
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0112.cnf') 
open(con);
sat_16 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_16[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_16 <- sat_16[9:226]
sat_16 <- lapply(sat_16, function(x) x[x != "0"])
sat_16 <- lapply(sat_16, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_16 = transform(sat_16)

#Check Literal Count 
count(sat_16)

close(con)

```

# Formula 17
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0113.cnf') 
open(con);
sat_17 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_17[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_17 <- sat_17[9:226]
sat_17 <- lapply(sat_17, function(x) x[x != "0"])
sat_17 <- lapply(sat_17, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_17 = transform(sat_17)

#Check Literal Count 
count(sat_17)

close(con)

```

# Formula 18 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0114.cnf') 
open(con);
sat_18 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_18[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_18 <- sat_18[9:226]
sat_18 <- lapply(sat_18, function(x) x[x != "0"])
sat_18 <- lapply(sat_18, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_18 = transform(sat_18)

#Check Literal Count 
count(sat_18)

close(con)

```

# Formula 19
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0115.cnf') 
open(con);
sat_19 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_19[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_19 <- sat_19[9:226]
sat_19 <- lapply(sat_19, function(x) x[x != "0"])
sat_19 <- lapply(sat_19, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_19 = transform(sat_19)

#Check Literal Count 
count(sat_19)

close(con)

```

# Formula 20
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0116.cnf') 
open(con);
sat_20 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_20[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_20 <- sat_20[9:226]
sat_20 <- lapply(sat_20, function(x) x[x != "0"])
sat_20 <- lapply(sat_20, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_20 = transform(sat_20)

#Check Literal Count 
count(sat_20)

close(con)

```
# TESTING SATISFIABILITY SET 
# Formula 1
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0203.cnf') 
open(con);
sat_21 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_21[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_21 <- sat_21[9:226]
sat_21 <- lapply(sat_21, function(x) x[x != "0"])
sat_21 <- lapply(sat_21, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_21 = transform(sat_21)

#Check Literal Count 
count(sat_21)

close(con)

```

# Formula 2
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0204.cnf') 
open(con);
sat_22 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_22[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_22 <- sat_22[9:226]
sat_22 <- lapply(sat_22, function(x) x[x != "0"])
sat_22 <- lapply(sat_22, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_22 = transform(sat_22)

#Check Literal Count 
count(sat_22)

close(con)

```

# Formula 3
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0205.cnf') 
open(con);
sat_23 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_23[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_23 <- sat_23[9:226]
sat_23 <- lapply(sat_23, function(x) x[x != "0"])
sat_23 <- lapply(sat_23, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_23 = transform(sat_23)

#Check Literal Count 
count(sat_23)

close(con)

```

# Formula 4
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0206.cnf') 
open(con);
sat_24 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_24[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_24 <- sat_24[9:226]
sat_24 <- lapply(sat_24, function(x) x[x != "0"])
sat_24 <- lapply(sat_24, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_24 = transform(sat_24)

#Check Literal Count 
count(sat_24)

close(con)

```
# Formula 5 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0211.cnf') 
open(con);
sat_25 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_25[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_25 <- sat_25[9:226]
sat_25 <- lapply(sat_25, function(x) x[x != "0"])
sat_25 <- lapply(sat_25, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_25 = transform(sat_25)

#Check Literal Count 
count(sat_25)

close(con)

```

# Formula 6 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0212.cnf') 
open(con);
sat_26 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_26[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_26 <- sat_26[9:226]
sat_26 <- lapply(sat_26, function(x) x[x != "0"])
sat_26 <- lapply(sat_26, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_26 = transform(sat_26)

#Check Literal Count 
count(sat_26)

close(con)

```

# Formula 7
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0300.cnf') 
open(con);
sat_27 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_27[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_27 <- sat_27[9:226]
sat_27 <- lapply(sat_27, function(x) x[x != "0"])
sat_27 <- lapply(sat_27, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_27 = transform(sat_27)

#Check Literal Count 
count(sat_27)

close(con)

```

# Formula 8 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0301.cnf') 
open(con);
sat_28 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_28[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_28 <- sat_28[9:226]
sat_28 <- lapply(sat_28, function(x) x[x != "0"])
sat_28 <- lapply(sat_28, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_28 = transform(sat_28)

#Check Literal Count 
count(sat_28)

close(con)

```

# Formula 9
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0302.cnf') 
open(con);
sat_29 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_29[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_29 <- sat_29[9:226]
sat_29 <- lapply(sat_29, function(x) x[x != "0"])
sat_29 <- lapply(sat_29, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_29 = transform(sat_29)

#Check Literal Count 
count(sat_29)

close(con)

```

# Formula 10 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0303.cnf') 
open(con);
sat_30 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_30[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_30 <- sat_30[9:226]
sat_30 <- lapply(sat_30, function(x) x[x != "0"])
sat_30 <- lapply(sat_30, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_30 = transform(sat_30)

#Check Literal Count 
count(sat_30)

close(con)

```

# Formula 11
```{r}
# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0304.cnf') 
open(con);
sat_31 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_31[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_31 <- sat_31[9:226]
sat_31 <- lapply(sat_31, function(x) x[x != "0"])
sat_31 <- lapply(sat_31, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_31 = transform(sat_31)

#Check Literal Count 
count(sat_31)

close(con)

```

# Formula 12
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0305.cnf') 
open(con);
sat_32 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_32[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_32 <- sat_32[9:226]
sat_32 <- lapply(sat_32, function(x) x[x != "0"])
sat_32 <- lapply(sat_32, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_32 = transform(sat_32)

#Check Literal Count 
count(sat_32)

close(con)

```

# Formula 13
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0306.cnf') 
open(con);
sat_33 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_33[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_33 <- sat_33[9:226]
sat_33 <- lapply(sat_33, function(x) x[x != "0"])
sat_33 <- lapply(sat_33, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_33 = transform(sat_33)

#Check Literal Count 
count(sat_33)

close(con)

```

# Formula 14
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0307.cnf') 
open(con);
sat_34 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_34[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_34 <- sat_34[9:226]
sat_34 <- lapply(sat_34, function(x) x[x != "0"])
sat_34 <- lapply(sat_34, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_34 = transform(sat_34)

#Check Literal Count 
count(sat_34)

close(con)

```

# Formula 15 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0309.cnf') 
open(con);
sat_35 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_35[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_35 <- sat_35[9:226]
sat_35 <- lapply(sat_35, function(x) x[x != "0"])
sat_35 <- lapply(sat_35, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_35 = transform(sat_35)

#Check Literal Count 
count(sat_35)

close(con)

```

# Formula 16 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0310.cnf') 
open(con);
sat_36 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_36[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_36 <- sat_36[9:226]
sat_36 <- lapply(sat_36, function(x) x[x != "0"])
sat_36 <- lapply(sat_36, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_36 = transform(sat_36)

#Check Literal Count 
count(sat_36)

close(con)

```

# Formula 17
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0312.cnf') 
open(con);
sat_37 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_37[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_37 <- sat_37[9:226]
sat_37 <- lapply(sat_37, function(x) x[x != "0"])
sat_37 <- lapply(sat_37, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_37 = transform(sat_37)

#Check Literal Count 
count(sat_37)

close(con)

```

# Formula 18 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0313.cnf') 
open(con);
sat_38 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_38[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_38 <- sat_38[9:226]
sat_38 <- lapply(sat_38, function(x) x[x != "0"])
sat_38 <- lapply(sat_38, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_38 = transform(sat_38)

#Check Literal Count 
count(sat_38)

close(con)

```

# Formula 19
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0315.cnf') 
open(con);
sat_39 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_39[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_39 <- sat_39[9:226]
sat_39 <- lapply(sat_39, function(x) x[x != "0"])
sat_39 <- lapply(sat_39, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_39 = transform(sat_39)

#Check Literal Count 
count(sat_39)

close(con)

```

# Formula 20 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/sat")
con <- file('uf50-0316.cnf') 
open(con);
sat_40 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  sat_40[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
sat_40 <- sat_40[9:226]
sat_40 <- lapply(sat_40, function(x) x[x != "0"])
sat_40 <- lapply(sat_40, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
sat_40 = transform(sat_40)

#Check Literal Count 
count(sat_40)

close(con)

```


#########################################################################################################
# Unsatisfiable Formulas
# 50 Variables, 218 Clauses 

# Formula 1 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-010.cnf') 
open(con);
unsat_1 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_1[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_1 <- unsat_1[9:226]
unsat_1 <- lapply(unsat_1, function(x) x[x != "0"])
unsat_1 <- lapply(unsat_1, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_1 = transform(unsat_1)

# Check Literal Count 
count(unsat_1)

close(con)

```

# Formula 2
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-01000.cnf') 
open(con);
unsat_2 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_2[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_2 <- unsat_2[9:226]
unsat_2 <- lapply(unsat_2, function(x) x[x != "0"])
unsat_2 <- lapply(unsat_2, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_2 = transform(unsat_2)

# Check Literal Count 
count(unsat_2)

close(con)

```

# Formula 3
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0101.cnf') 
open(con);
unsat_3 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_3[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_3 <- unsat_3[9:226]
unsat_3 <- lapply(unsat_3, function(x) x[x != "0"])
unsat_3 <- lapply(unsat_3, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_3 = transform(unsat_3)

# Check Literal Count 
count(unsat_3)

close(con)

```

# Formula 4 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0102.cnf') 
open(con);
unsat_4 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_4[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_4 <- unsat_4[9:226]
unsat_4 <- lapply(unsat_4, function(x) x[x != "0"])
unsat_4 <- lapply(unsat_4, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_4 = transform(unsat_4)

# Check Literal Count 
count(unsat_4)

close(con)

```

# Formula 5
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0103.cnf') 
open(con);
unsat_5 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_5[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_5 <- unsat_5[9:226]
unsat_5 <- lapply(unsat_5, function(x) x[x != "0"])
unsat_5 <- lapply(unsat_5, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_5 = transform(unsat_5)

# Check Literal Count 
count(unsat_5)

close(con)

```

# Formula 6
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0105.cnf') 
open(con);
unsat_6 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_6[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_6 <- unsat_6[9:226]
unsat_6 <- lapply(unsat_6, function(x) x[x != "0"])
unsat_6 <- lapply(unsat_6, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_6 = transform(unsat_6)

# Check Literal Count 
count(unsat_6)

close(con)

```


# Formula 7
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0106.cnf') 
open(con);
unsat_7 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_7[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_7 <- unsat_7[9:226]
unsat_7 <- lapply(unsat_7, function(x) x[x != "0"])
unsat_7 <- lapply(unsat_7, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_7 = transform(unsat_7)

# Check Literal Count 
count(unsat_7)

close(con)

```

# Formula 8
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0107.cnf') 
open(con);
unsat_8 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_8[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_8 <- unsat_8[9:226]
unsat_8 <- lapply(unsat_8, function(x) x[x != "0"])
unsat_8 <- lapply(unsat_8, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_8 = transform(unsat_8)

# Check Literal Count 
count(unsat_8)

close(con)

```

# Formula 9
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0108.cnf') 
open(con);
unsat_9 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_9[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_9 <- unsat_9[9:226]
unsat_9 <- lapply(unsat_9, function(x) x[x != "0"])
unsat_9 <- lapply(unsat_9, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_9 = transform(unsat_9)

# Check Literal Count 
count(unsat_9)

close(con)

```

# Formula 10
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0109.cnf') 
open(con);
unsat_10 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_10[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_10 <- unsat_10[9:226]
unsat_10 <- lapply(unsat_10, function(x) x[x != "0"])
unsat_10 <- lapply(unsat_10, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_10 = transform(unsat_10)

# Check Literal Count 
count(unsat_10)

close(con)

```

# Formula 11
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-011.cnf') 
open(con);
unsat_11 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_11[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_11 <- unsat_11[9:226]
unsat_11 <- lapply(unsat_11, function(x) x[x != "0"])
unsat_11 <- lapply(unsat_11, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_11 = transform(unsat_11)

# Check Literal Count 
count(unsat_11)

close(con)

```

# Formula 12
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0111.cnf') 
open(con);
unsat_12 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_12[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_12 <- unsat_12[9:226]
unsat_12 <- lapply(unsat_12, function(x) x[x != "0"])
unsat_12 <- lapply(unsat_12, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_12 = transform(unsat_12)

# Check Literal Count 
count(unsat_12)

close(con)

```

# Formula 13
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0112.cnf') 
open(con);
unsat_13 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_13[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_13 <- unsat_13[9:226]
unsat_13 <- lapply(unsat_13, function(x) x[x != "0"])
unsat_13 <- lapply(unsat_13, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_13 = transform(unsat_13)

# Check Literal Count 
count(unsat_13)

close(con)

```

# Formula 14
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0113.cnf') 
open(con);
unsat_14 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_14[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_14 <- unsat_14[9:226]
unsat_14 <- lapply(unsat_14, function(x) x[x != "0"])
unsat_14 <- lapply(unsat_14, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_14 = transform(unsat_14)

# Check Literal Count 
count(unsat_14)

close(con)

```

# Formula 15 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0115.cnf') 
open(con);
unsat_15 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_15[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_15 <- unsat_15[9:226]
unsat_15 <- lapply(unsat_15, function(x) x[x != "0"])
unsat_15 <- lapply(unsat_15, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_15 = transform(unsat_15)

# Check Literal Count 
count(unsat_15)

close(con)

```

# Formula 16 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0116.cnf') 
open(con);
unsat_16 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_16[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_16 <- unsat_16[9:226]
unsat_16 <- lapply(unsat_16, function(x) x[x != "0"])
unsat_16 <- lapply(unsat_16, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_16 = transform(unsat_16)

# Check Literal Count 
count(unsat_16)

close(con)

```

# Formula 17
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0117.cnf') 
open(con);
unsat_17 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_17[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_17 <- unsat_17[9:226]
unsat_17 <- lapply(unsat_17, function(x) x[x != "0"])
unsat_17 <- lapply(unsat_17, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_17 = transform(unsat_17)

# Check Literal Count 
count(unsat_17)

close(con)

```

# Formula 18 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0118.cnf') 
open(con);
unsat_18 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_18[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_18 <- unsat_18[9:226]
unsat_18 <- lapply(unsat_18, function(x) x[x != "0"])
unsat_18 <- lapply(unsat_18, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_18 = transform(unsat_18)

# Check Literal Count 
count(unsat_18)

close(con)

```

# Formula 19
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0119.cnf') 
open(con);
unsat_19 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_19[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_19 <- unsat_19[9:226]
unsat_19 <- lapply(unsat_19, function(x) x[x != "0"])
unsat_19 <- lapply(unsat_19, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_19 = transform(unsat_19)

# Check Literal Count 
count(unsat_19)

close(con)

```

# Formula 20 
```{r}

# Open File
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0120.cnf') 
open(con);
unsat_20 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_20[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_20 <- unsat_20[9:226]
unsat_20 <- lapply(unsat_20, function(x) x[x != "0"])
unsat_20 <- lapply(unsat_20, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_20 = transform(unsat_20)

# Check Literal Count 
count(unsat_20)

close(con)

```


# TESTING UNSATISFIABILITY 
# Formula 1
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0301.cnf') 
open(con);
unsat_21 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_21[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_21 <- unsat_21[9:226]
unsat_21 <- lapply(unsat_21, function(x) x[x != "0"])
unsat_21 <- lapply(unsat_21, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_21 = transform(unsat_21)

# Check Literal Count 
count(unsat_21)

close(con)

```

# Formula 2
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0302.cnf') 
open(con);
unsat_22 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_22[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_22 <- unsat_22[9:226]
unsat_22 <- lapply(unsat_22, function(x) x[x != "0"])
unsat_22 <- lapply(unsat_22, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_22 = transform(unsat_22)

# Check Literal Count 
count(unsat_22)

close(con)

```

# Formula 3
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0303.cnf') 
open(con);
unsat_23 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_23[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_23 <- unsat_23[9:226]
unsat_23 <- lapply(unsat_23, function(x) x[x != "0"])
unsat_23 <- lapply(unsat_23, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_23 = transform(unsat_23)

# Check Literal Count 
count(unsat_23)

close(con)

```

# Formula 4
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0304.cnf') 
open(con);
unsat_24 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_24[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_24 <- unsat_24[9:226]
unsat_24 <- lapply(unsat_24, function(x) x[x != "0"])
unsat_24 <- lapply(unsat_24, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_24 = transform(unsat_24)

# Check Literal Count 
count(unsat_24)

close(con)

```

# Formula 5 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0305.cnf') 
open(con);
unsat_25 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_25[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_25 <- unsat_25[9:226]
unsat_25 <- lapply(unsat_25, function(x) x[x != "0"])
unsat_25 <- lapply(unsat_25, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_25 = transform(unsat_25)

# Check Literal Count 
count(unsat_25)

close(con)

```

# Formula 6 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0306.cnf') 
open(con);
unsat_26 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_26[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_26 <- unsat_26[9:226]
unsat_26 <- lapply(unsat_26, function(x) x[x != "0"])
unsat_26 <- lapply(unsat_26, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_26 = transform(unsat_26)

# Check Literal Count 
count(unsat_26)

close(con)

```

# Formula 7
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0307.cnf') 
open(con);
unsat_27 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_27[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_27 <- unsat_27[9:226]
unsat_27 <- lapply(unsat_27, function(x) x[x != "0"])
unsat_27 <- lapply(unsat_27, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_27 = transform(unsat_27)

# Check Literal Count 
count(unsat_27)

close(con)

```

# Formula 8 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0415.cnf') 
open(con);
unsat_28 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_28[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_28 <- unsat_28[9:226]
unsat_28 <- lapply(unsat_28, function(x) x[x != "0"])
unsat_28 <- lapply(unsat_28, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_28 = transform(unsat_28)

# Check Literal Count 
count(unsat_28)

close(con)

```

# Formula 9
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0517.cnf') 
open(con);
unsat_29 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_29[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_29 <- unsat_29[9:226]
unsat_29 <- lapply(unsat_29, function(x) x[x != "0"])
unsat_29 <- lapply(unsat_29, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_29 = transform(unsat_29)

# Check Literal Count 
count(unsat_29)

close(con)

```

# Formula 10 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0518.cnf') 
open(con);
unsat_30 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_30[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_30 <- unsat_30[9:226]
unsat_30 <- lapply(unsat_30, function(x) x[x != "0"])
unsat_30 <- lapply(unsat_30, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_30 = transform(unsat_30)

# Check Literal Count 
count(unsat_30)

close(con)

```

# Formula 11
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0519.cnf') 
open(con);
unsat_31 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_31[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_31 <- unsat_31[9:226]
unsat_31 <- lapply(unsat_31, function(x) x[x != "0"])
unsat_31 <- lapply(unsat_31, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_31 = transform(unsat_31)

# Check Literal Count 
count(unsat_31)

close(con)

```

# Formula 12
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0520.cnf') 
open(con);
unsat_32 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_32[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_32 <- unsat_32[9:226]
unsat_32 <- lapply(unsat_32, function(x) x[x != "0"])
unsat_32 <- lapply(unsat_32, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_32 = transform(unsat_32)

# Check Literal Count 
count(unsat_32)

close(con)

```

# Formula 13
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0521.cnf') 
open(con);
unsat_33 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_33[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_33 <- unsat_33[9:226]
unsat_33 <- lapply(unsat_33, function(x) x[x != "0"])
unsat_33 <- lapply(unsat_33, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_33 = transform(unsat_33)

# Check Literal Count 
count(unsat_33)

close(con)

```

# Formula 14
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0522.cnf') 
open(con);
unsat_34 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_34[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_34 <- unsat_34[9:226]
unsat_34 <- lapply(unsat_34, function(x) x[x != "0"])
unsat_34 <- lapply(unsat_34, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_34 = transform(unsat_34)

# Check Literal Count 
count(unsat_34)

close(con)

```

# Formula 15 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0523.cnf') 
open(con);
unsat_35 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_35[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_35 <- unsat_35[9:226]
unsat_35 <- lapply(unsat_35, function(x) x[x != "0"])
unsat_35 <- lapply(unsat_35, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_35 = transform(unsat_35)

# Check Literal Count 
count(unsat_35)

close(con)

```

# Formula 16 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0525.cnf') 
open(con);
unsat_36 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_36[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_36 <- unsat_36[9:226]
unsat_36 <- lapply(unsat_36, function(x) x[x != "0"])
unsat_36 <- lapply(unsat_36, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_36 = transform(unsat_36)

# Check Literal Count 
count(unsat_36)

close(con)

```

# Formula 17
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0526.cnf') 
open(con);
unsat_37 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_37[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_37 <- unsat_37[9:226]
unsat_37 <- lapply(unsat_37, function(x) x[x != "0"])
unsat_37 <- lapply(unsat_37, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_37 = transform(unsat_37)

# Check Literal Count 
count(unsat_37)

close(con)

```

# Formula 18 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0527.cnf') 
open(con);
unsat_38 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_38[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_38 <- unsat_38[9:226]
unsat_38 <- lapply(unsat_38, function(x) x[x != "0"])
unsat_38 <- lapply(unsat_38, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_38 = transform(unsat_38)

# Check Literal Count 
count(unsat_38)

close(con)

```

# Formula 19
```{r}
setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0528.cnf') 
open(con);
unsat_39 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_39[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_39 <- unsat_39[9:226]
unsat_39 <- lapply(unsat_39, function(x) x[x != "0"])
unsat_39 <- lapply(unsat_39, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_39 = transform(unsat_39)

# Check Literal Count 
count(unsat_39)

close(con)

```

# Formula 20 
```{r}

setwd("C:/Users/dmo/Documents/MachineLearning/Project/dimacs/unsat")
con <- file('uuf50-0550.cnf') 
open(con);
unsat_40 <- list();
current.line <- 1
while (length(line <- readLines(con, n = 1, warn = FALSE)) > 0) {
  unsat_40[[current.line]] <- as.integer(unlist(strsplit(line, split=" ")))
  current.line <- current.line + 1
} 

# Process Data
unsat_40 <- unsat_40[9:226]
unsat_40 <- lapply(unsat_40, function(x) x[x != "0"])
unsat_40 <- lapply(unsat_40, function(x) x[!is.na(x)])

# Transform to Sparse Matrix
unsat_40 = transform(unsat_40)

# Check Literal Count 
count(unsat_40)

close(con)

```

